---
title: "PM566 Assignment 05"
author: "Luqing Ren"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

This is my PM566 Assignment. I will showcase a few interactive visuals here.

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

<br>

```{r load-data,,echo=FALSE}
data <- read_csv("map.csv")
data1<- read_csv("census_2.csv")
```

<br>

## First step {.tabset}

```{r,echo=FALSE}
p<- 
  plot_ly(data1, x = ~as.factor(community_cat), y = ~cardio,alpha = 0.1) %>% 
  add_boxplot(color = ~community_cat) %>%
  layout(title ="cardiovascular rate by community category ",
         legend_title = "dis",
         yaxis = list(title = "cardiovascular rate"), 
         xaxis = list(title = "disadvantage community"))
p %>% hide_legend()
```
Figure1 : Cardiovascular disease occurrence rate by community category. 
 
 

```{r plot1, class.source="code-r-small",,echo=FALSE}

p1_scatter <- data %>% 
  plot_ly(x = ~PM2.5_mean, y = ~cardio_mean,
          type = 'scatter', mode = 'markers', color = ~county_name,
          size = ~PM2.5_mean, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          text = ~paste( paste("County: ", county_name, sep=""), paste(" PM2.5 value: ", PM2.5_mean, sep="") , paste("cardiovascular rate : ", cardio_mean, sep=""), sep = "<br>")) %>%
  layout(title = "Cardiovascular rate vs. pollutant PM2.5",
                yaxis = list(title = "cardiovascular rate"), 
         xaxis = list(title = "PM2.5"),hovermode = "compare")

p2_scatter <- data %>% 
  plot_ly(x = ~ozone_mean, y = ~cardio_mean,
          type = 'scatter', mode = 'markers', color = ~county_name,
          size = ~ozone_mean, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          text = ~paste( paste("County: ", county_name, sep=""), paste(" Ozone value: ", ozone_mean, sep="") , paste("cardiovascular rate : ", cardio_mean, sep=""), sep = "<br>")) %>%
  layout(title = "Cardiovascular rate vs. pollutant Ozone",
                yaxis = list(title = "cardiovascular rate"), 
         xaxis = list(title = "Ozone"),hovermode = "compare")

```

<br>

## Second step {.tabset}

Create tabs to display each figure

### Scatterplot: with PM2.5

```{r p1}
p1_scatter
```

### Scatterplot: without Ozone

```{r p2}
p2_scatter
```

## {-}

Figure2: The correlation within cardiovascular rate and pollution indicators: PM2.5 and Ozone.

<br>

## Third step {.tabset}
```{r,echo=FALSE}
map_data <- read.csv("new.csv")
to_map<-as.data.table(map_data)[, .SD[1], by="county_name"]
fig <- to_map 
fig <- fig %>%
  plot_ly(
    lat = ~lat,
    lon = ~long,
    marker = list(color = "fuchsia"),
    type = 'scattermapbox',
    text = ~paste( paste(county_name, sep=""), paste("Cardiovascular rate : ", cardio_mean, sep=""), paste("Pollution score: ", pol_score, sep=""), sep = "<br>"))
   
fig <- fig %>%
  layout(
    mapbox = list(
      style = 'open-street-map',
      zoom =2.5,
      center = list(lon = -118.9408, lat = 34.07497))) 
fig
```
Figure3: A map shows the pollution score and cardiovascular rate data of each county in California. 

Done!

<br>
<br>