---
title: "HW03"
author: "Luqing Ren"
date: "10/13/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## APIs
```{r counter-pubmed, eval=TRUE}
library(data.table)
library(tidyverse)
library(xml2)
library(httr)
library(stringr)
# Using the NCBI API, look for papers that show up under the term "sars-cov-2 trial vaccine."Look for the data in the pubmed database.How many papers were you able to find?

# Downloading the website
website<- read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine")
# Finding the counts
counts <- xml_find_first(website,"/html/body/main/div[9]/div[2]/div[2]/div[1]/span")
# Turning it into text
counts <- as.character(counts)
# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```

- There are 560 papers with term "sars-cov-2 trial vaccine".

```{r query ids, eval=TRUE}
# get academic publications
#Using the list of pubmed ids you retrieved, download each papers’ details using the query parameter rettype = abstract. If you get more than 250 ids, just keep the first 250.
query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(db ="pubmed",
  term ="sars-cov-2 trial vaccine",
   retmax = 1000
  )
   )
# Extracting the content of the response of GET
ids <- content(query_ids)
```

```{r get-details, eval=TRUE}
# Turn the result into a character vector
ids <- as.character(ids)
cat(ids)
# Find all the ids 
ids <- str_extract_all(ids, "<Id>[0-9]+</Id>") 
ids<-ids [[1]]
# Remove all the leading and trailing <Id> </Id>. Make use of "|"
ids <- stringr::str_remove_all(ids, "<Id>|</Id>")
```

- I get 227 ids.

```{r get-abstracts, eval = TRUE}
publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
          db= "pubmed",
          id = paste(ids, collapse = ","),
          retmax = 1000,
          rettype ="abstract" 
          )
)
publications
# Turning the output into character vector
publications <- content(publications)
publications_txt <- as.character(publications)
```

```{r one-string-per-response, eval = TRUE}
#We will use the `xml2::xml_children()` function to keep one element per id.
pub_char_list <- xml2::xml_children(publications)
pub_char_list <- sapply(pub_char_list, as.character)
```

```{r extracting-last-bit, eval = TRUE}
# extract the abstract for each one of the elements of `pub_char_list`.
abstracts <- str_extract(pub_char_list, "<Abstract>(\\n|.)+</Abstract>")
abstracts <- str_remove_all(abstracts, "</?[[:alnum:]]+>")
abstracts <- str_replace_all(abstracts, "\\s+"," ")
```

```{r process-titles, eval = TRUE}
titles <- str_extract(pub_char_list, "<ArticleTitle>(\\n|.)+</ArticleTitle>")
titles <- str_remove_all(titles, "</?[[:alnum:]]+>")
titles <- str_replace_all(titles, "\\s+"," ")
```

```{r process-dates, eval = TRUE}
dates <- str_extract(pub_char_list, "<PubDate>(\\n|.)+</PubDate>")
dates <- str_remove_all(dates, "</?[[:alnum:]]+>")
dates <- str_replace_all(dates, "\\s+"," ")
```

```{r process-journal, eval = TRUE}
journal <- str_extract(pub_char_list, "<Title>(\\n|.)+</Title>")
journal <- str_remove_all(journal, "</?[[:alnum:]]+>")
journal <- str_replace_all(journal, "\\s+"," ")
```

```{r build-db, eval = TRUE}
# put everything together into a single data frame.
dataset <- data.frame(
  PubMedID = ids,
  Title = titles,
  Abstracts = abstracts,
  Journal =journal,
  Data= dates
)
knitr::kable(dataset[1:3,])  # show the first three.
```

## Text Mining
1.Tokenize the abstracts and count the number of each token.Do you see anything interesting? Does removing stop words change what tokens appear as the most frequent? What are the 5 most common tokens for each search term after removing stopwords?
```{r tokenize-count, eval = TRUE}
# read the material
library(readr)
library(dplyr)
library(ggplot2)
library(tidytext)
library(tidyverse)
data <- read_csv("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/03_pubmed/pubmed.csv")

#tokenize the abstracts and count
  data %>% 
  unnest_tokens(token,abstract) %>% 
  group_by(term) %>% 
  count(token,sort= TRUE) %>% 
  top_n(5,n)
  
# remove stop words and number
nums <- as.character(seq(0,100))
data %>% 
unnest_tokens(word, abstract) %>%
group_by(term) %>% 
filter(!(word %in% nums)) %>% 
anti_join(stop_words, by= c("word")) %>% 
count(word, sort = TRUE) %>% 
top_n(5,n) 

```
- The top 5 most frequent words almost are stop words.After removing stop words, the top 5 most frequent words are looks reliable.
- The top 5 most common tokens after removing stopwords of "covid" search term are : covid, patients,disease,pandemic,coronavirus,health
- The top 5 most common tokens after removing stopwords of "prostate cancer"search term are : cancer,prostate,patients,treatments,disease
- The top 5 most common tokens after removing stopwords of "preeclampsia"search term are : pre,eclampsia,preeclampsia,women,pregnancy
- The top 5 most common tokens after removing stopwords of "cystic fibrosis"search term are : fibrosis,cystic,cf,patients,disease
- The top 5 most common tokens after removing stopwords of "meningitis"search term are : patients,meningitis,meningeal,csf,clinical

```{r bigram, eval = TRUE}
## Tokenize the abstracts into bigrams.Find the 10 most common bigram and visualize them with ggplot2.
data %>% 
  unnest_ngrams(token,abstract, 2 ) %>% 
  count(token,sort= TRUE) %>% 
  top_n(10,n) %>% 
  ggplot(aes(n,fct_reorder(token,n)))+
  geom_col()
```

- The phrase are not much descriptive with bigrams.

```{r eval = TRUE}
# Calculate the TF-IDF value for each word-search term combination. (here you want the search term to be the “document”) What are the 5 tokens from each search term with the highest TF-IDF value? How are the results different from the answers you got in question 1?

data %>% 
  unnest_tokens(token, abstract) %>% 
  group_by(term) %>% 
  filter(!(token %in% nums)) %>% 
  count(token, term) %>% 
  bind_tf_idf(token,term,n) %>% 
  arrange(desc(tf_idf)) 
```

- The top 5 tokens with the highest TF-IDF value of "covid"search term: covid, pandemic, coronavirus, sars, cov
- The top 5 tokens with the highest TF-IDF value of "prostate cancer"search term: prostate, androgen, psa, prostatectomy,castration
- The top 5 tokens with the highest TF-IDF value of "preeclampsia"search term: eclampsia, preeclampsia, pregnancy,maternal,gestational
- The top 5 tokens with the highest TF-IDF value of "cystic fibrosis"search term: cf, fibrosis, cystic, cftr, sweat
- The top 5 tokens with the highest TF-IDF value of "meningitis"search term: meningitis, meningeal, pachymeningitis,csf,meninges

- These top 5 tokens words with the highest TF-IDF value are more related to the search term than token words got in question 1. For instance, in "prostate cancer"search term, we got "androgen", "psa", "prostatectomy","castration" these specialized words.





